### 2020-02-14 README.Rmd
Better clarification of the validation process.

@@

@@

>>>>

### Example: Validating AFINN using the gold standard

@@

As instructed, put back the score you would like to validate into the `docvars` "target_value". In this example, we calculate the AFINN score for each tweet using quanteda. The dictionary `afinn` is bundle with this package.

@@

Put back the vector of AFINN score into the respective `docvars` and study the correlation between the gold standard and AFINN.
